---
title: "R Notebook"
output: html_notebook
---

```{r}
## Import libraries

# save default plot params so we can reset the plot window

gpars<-par()
i=match(c("cin","cra","csi","cxy","din","page"),names(gpars))
gpars<-gpars[-i]

# load libraries

library(MASS)
library(mnem)       # needed for transitive.reduction/closure
library(igraph) 
library(Rgraphviz)
library(graph) 
library(coda)       # for MCMC output analysis
library(lecount)    # count linear extensions of a PO
library(partitions) # used by dimension functions
library(parallel)

#replace this with your working directory
#wd<-
#setwd(wd)

# load function files

source(file="pofun.R")
source(file="pofun_aux.R")
source(file="modelfun.R")
source(file="dimfun.R")
source(file="my_code.R")
```

Runtime plots
```{r}
set.seed(10)
results2 <- vector("list",3)
for (i in 1:3){
  results2[[i]] <- vector("list",8)
}
time.spent <- matrix(0,3,8,dimnames = list(10*(1:3),5*(1:8)))

library(parallel)

cl <- makeCluster(min(24,detectCores() - 1))


# load libraries and source files on each worker
clusterEvalQ(cl, {
  library(MASS)
  library(mnem)       # needed for transitive.reduction/closure
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)       # for MCMC output analysis
  library(lecount)    # count linear extensions of a PO
  library(partitions) # used by dimension functions
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
})


# independent random-number streams
clusterSetRNGStream(cl, 10)


# create all 24 combinations of i and j
jobs <- expand.grid(
  i = 1:8,
  j = 1:3
)

N <- 30

m <- mc <- b <- vector("list",8)

for (i in 1:8){
  m[[i]] <- rZPO(5*i)
  mc[[i]] <- my.transitive.closure(m[[i]])
  b[[i]] <- rgeom.bucket.from.po(mc[[i]],n.samples = N,p=.5,suborder=T,noise.prob = .02);
}


clusterExport(cl, c("jobs","m","mc","b"))

results2p <- parLapply(cl, 1:nrow(jobs), function(k){
  
  i <- jobs$i[k]
  j <- jobs$j[k]
  
  n <- as.integer(5*i); burn <- 0; thin <- 1; n.samples <- 1e4; p <- 0.02
  
  start.time <- Sys.time()
  out <- rposterior.bucket(n=n, b=b[[i]][1:(10*j)], n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm = T, r=.5, noise.prob =p) 
  end.time <- Sys.time()
  
  time <- as.numeric(difftime(end.time, start.time, units="secs"))
  
  list(
    i=i,
    j=j,
    out=out,
    time=time
  )
})


# put results back into original 3 x 8 structure
for (k in 1:length(results2p)){
  
  i <- results2p[[k]]$i
  j <- results2p[[k]]$j
  
  results2[[j]][[i]] <- results2p[[k]]$out
  time.spent[j,i] <- results2p[[k]]$time
  
}

stopCluster(cl)
```


4.1, 4.2
```{r}
#Distance Frequency plot
max.ham <- max(sapply(result3.data$ham,function(x) max(as.numeric(names(x)))))
ham.dist.mat <- matrix(0,8,max.ham+1)

for (i in 1:8){
  lab <- as.numeric(names(result3.data$ham[[i]]))
  ham.dist.mat[i,lab+1] <- as.numeric(result3.data$ham[[i]])
}

plot(0:max.ham,ham.dist.mat[1,],type="l",xlim=c(0,max.ham),col=adjustcolor("black",alpha.f=.4),ylab="Frequency",xlab="Hamming distance",ylim=c(0,40000))
for (i in 2:8){
  lines(0:max.ham,ham.dist.mat[i,],col=adjustcolor("black",alpha.f=.4))
}
title("Frequency of Hamming distance to true partial order")

#Hamming dist plot
p <- 0
v <- matrix(0,8,101)
for (k in 1:8){
  meanpo <- result3.data$mean[[k]]
  for (i in 0:100){
    v[k,i+1] <- hamming.dist(consensus.po2(meanpo,i/100),code1.m)
  }
  if (k==1) plot((0:100)/100,v[k,],type="l",ylab="hamming dist",xlab="p",col=adjustcolor("black",alpha.f=.7))
  if (k!=1) lines((0:100)/100,v[k,],type="l",col=adjustcolor("black",alpha.f=.7))
  title("Hamming dist of 8 p-consensus against p")
  opt.p <- (which(v[k,]==min(v[k,]))-1)/100
  opt.range <- c(min(opt.p),max(opt.p))
  min.dist <- v[k,][opt.p[1]*100+1]
  p <- p + max(opt.p)/8
  cat(c("\n At i=",k,", minimum dist is last achieved at p=",max(opt.p),", where the hamming distance is",min.dist,". \n At p=1/3, the hamming dist is ",v[k,34],"."))
}
cat(c("\n average maximal opt p is ",p))

#ESS
#took 1.73 hours to run :(
st <- Sys.time()

burn <- 1e5
n.samples <- 1e6
sample.ind <- (burn + 1):n.samples

ess.list <- vector("list", 8)
min.ess <- numeric(8)

for (k in 1:8) {

  samples <- result3$out[[k]]$samples

  ess <- matrix(Inf, n, n)

  for (i in 1:n) {
    for (j in 1:n) {
      
      print(c(i,j,k))
      if (i == j)
        next

      v <- vapply(
        sample.ind,
        function(t) samples[[t]][i,j],
        numeric(1)
      )

      if (var(v) != 0)
        ess[i,j] <- effectiveSize(v)
    }
  }

  ess.list[[k]] <- ess
  min.ess[k] <- min(ess)

}

et <- Sys.time()
timepassed <- et - st
```



4.3
```{r}
## Import libraries

# save default plot params so we can reset the plot window
gpars<-par()
i=match(c("cin","cra","csi","cxy","din","page"),names(gpars))
gpars<-gpars[-i]

# load libraries
library(MASS)
library(mnem)       # needed for transitive.reduction/closure
library(igraph) 
library(Rgraphviz)
library(graph) 
library(coda)       # for MCMC output analysis
library(lecount)    # count linear extensions of a PO
library(partitions) # used by dimension functions
library(parallel)

#working directory
#wd<-#"C:/Users/oweny_djchlla/OneDrive/Desktop/Posim 2 simulation"
#setwd(wd)

# load function files
source(file="pofun.R")
source(file="pofun_aux.R")
source(file="modelfun.R")
source(file="dimfun.R")
source(file="my_code.R")
source(file="code data.R")
```

Generating data
```{r}
#n=10
n <- 10L; N <- 40; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05

#m <- rZPO(n)
m <- matrix(c(0,0,0,1,0,0,1,1,0,1,1,0,1,1,0,0,1,1,0,1,1,0,0,1,0,0,1,1,0,1,0,0,0,0,0,0,0,0,0,0,1,0,1,1,0,0,1,1,0,1,1,1,1,1,0,0,1,1,1,1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,1,0,0,1,1,0,1,0,0,0,0,0,0,0,1,0,0), nrow=10, byrow=TRUE)
mc <- my.transitive.closure(m); mr <- transitive.reduction(m)
showDAG(t(mr)); title(paste(c("depth =",dag.depth(mr,10)),collapse = " "))

true.po.10 <- m
buckets.10 <- rgeom.bucket.from.po(mc,n.samples = N,p=.5,suborder=T,noise.prob = p)

#n=20
n <- 20L; N <- 40; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05

#m <- rZPO(n)
m <- matrix(c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,1,0,0,0,1,0,1,0,1,1,0,0,1,1,0,1,1,1,1,0,1,0,1,1,1,0,0,0,1,0,0,0,1,1,0,1,1,1,1,0,1,0,1,1,1,0,1,0,0,0,1,1,0,0,1,0,1,0,1,1,1,1,1,1,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,1,0,1,1,1,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,1,0,0,0,1,1,1,0,1,1,0,0,1,1,0,1,1,1,1,0,1,0,1,1,1,0,0,0,0,0,0,0,0,1,1,0,0,1,0,1,0,1,0,0,0,0,0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0,1,0,0,1,0,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,1,1,0,0,1,0,1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,1,0,1,1,0,0,1,1,0,1,1,1,1,0,1,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,1,1,0,0,1,0,1,0,1,0,1,0,1,1,0,0,1,1,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,1,1,0,0,1,0,1,0,1,0), nrow=20, byrow=TRUE)
mc <- my.transitive.closure(m); mr <- transitive.reduction(m)
showDAG(t(mr)); title(paste(c("depth =",dag.depth(mr,20)),collapse = " "))

true.po.20 <- m
buckets.20 <- rgeom.bucket.from.po(mc,n.samples = N,p=.5,suborder=T,noise.prob = p)

#n=30
n <- 30L; N <- 40; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05

#m <- rZPO(n)
m <- rbind(c(0,1,1,0,0,1,0,1,1,1,0,0,1,1,1,0,0,1,1,1,1,1,0,0,1,0,1,0,1,1),c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),c(0,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),c(1,1,1,0,0,1,0,1,1,1,0,0,1,1,1,0,1,1,1,1,1,1,0,1,1,1,1,0,1,1),c(1,1,1,0,0,1,0,1,1,1,1,0,1,1,1,0,1,1,1,1,1,1,0,1,1,1,1,0,1,1),c(0,1,1,0,0,0,0,1,1,1,0,0,1,0,0,0,0,0,1,0,1,0,0,0,0,0,0,0,0,1),c(1,1,1,0,0,1,0,1,1,1,1,0,1,1,1,0,1,1,1,1,1,1,0,1,1,1,1,0,1,1),c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),c(0,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),c(0,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),c(0,1,1,0,0,1,0,1,1,1,0,0,1,1,1,0,0,1,1,1,1,1,0,0,1,0,1,0,1,1),c(1,1,1,1,1,1,1,1,1,1,1,0,1,1,1,1,1,1,1,1,1,1,0,1,1,1,1,1,1,1),c(0,1,1,0,0,0,0,1,1,1,0,0,0,0,0,0,0,0,1,0,1,0,0,0,0,0,0,0,0,1),c(0,1,1,0,0,1,0,1,1,1,0,0,1,0,1,0,0,0,1,1,1,1,0,0,0,0,0,0,0,1),c(0,1,1,0,0,0,0,1,1,1,0,0,1,0,0,0,0,0,1,0,1,0,0,0,0,0,0,0,0,1),c(1,1,1,0,0,1,0,1,1,1,1,0,1,1,1,0,1,1,1,1,1,1,0,1,1,1,1,0,1,1),c(0,1,1,0,0,1,0,1,1,1,0,0,1,1,1,0,0,1,1,1,1,1,0,0,1,0,1,0,1,1),c(0,1,1,0,0,0,0,1,1,1,0,0,1,0,0,0,0,0,1,1,1,0,0,0,0,0,0,0,0,1),c(0,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),c(0,1,1,0,0,0,0,1,1,1,0,0,1,0,0,0,0,0,1,0,1,0,0,0,0,0,0,0,0,1),c(0,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),c(0,1,1,0,0,0,0,1,1,1,0,0,1,0,0,0,0,0,1,0,1,0,0,0,0,0,0,0,0,1),c(1,1,1,1,1,1,1,1,1,1,1,0,1,1,1,1,1,1,1,1,1,1,0,1,1,1,1,1,1,1),c(0,1,1,0,0,1,0,1,1,1,0,0,1,1,1,0,0,1,1,1,1,1,0,0,1,0,1,0,1,1),c(0,1,1,0,0,1,0,1,1,1,0,0,1,0,1,0,0,1,1,1,1,1,0,0,0,0,0,0,0,1),c(0,1,1,0,0,1,0,1,1,1,0,0,1,1,1,0,0,1,1,1,1,1,0,0,1,0,1,0,1,1),c(0,1,1,0,0,0,0,1,1,1,0,0,1,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,1),c(1,1,1,0,0,1,0,1,1,1,1,0,1,1,1,0,1,1,1,1,1,1,0,1,1,1,1,0,1,1),c(0,1,1,0,0,1,0,1,1,1,0,0,1,0,1,0,0,1,1,1,1,1,0,0,0,0,0,0,0,1),c(0,1,0,0,0,0,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)); rownames(m) <- colnames(m) <- 1:30
mc <- my.transitive.closure(m); mr <- transitive.reduction(m)
showDAG(t(mr)); title(paste(c("depth =",dag.depth(mr,30)),collapse = " "))

true.po.30 <- m
buckets.30 <- rgeom.bucket.from.po(mc,n.samples = N,p=.5,suborder=T,noise.prob = p)

#empty po
n <- 24L; N <- 30; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05
empty.po <- matrix(0, nrow=n, ncol=n, byrow=TRUE, dimnames = list(1:n,1:n))
buckets.emp <- rgeom.bucket.from.po(empty.po,n.samples = N,p=.5,suborder=T,noise.prob = p)

#total order
n <- 24L
total.order <- seqtodag(1:n,n); rownames(total.order) <- colnames(total.order) <- 1:n
buckets.total <- rgeom.bucket.from.po(total.order,n.samples = N,p=.5,suborder=T,noise.prob = p)

```

```{r}
n <- 24L; N <- 30; burn <- 1e4; thin <- 1; n.samples <- 1e5; p <- 0.05

cl <- makeCluster(20)

clusterExport(cl,c("n","N","burn","thin","n.samples","p"))

clusterEvalQ(cl,{
  library(MASS)
  library(mnem)
  library(igraph)
  library(Rgraphviz)
  library(graph)
  library(coda)
  library(lecount)
  library(partitions)
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
  
  check.dag <- function(mc){!any(mc+t(mc)==2)}
})

clusterSetRNGStream(cl,10)

true.po <- parLapply(cl,1:10,function(j){
  m <- rZPO(n)
  my.transitive.closure(m)
})

clusterExport(cl,c("n","N","burn","thin","n.samples","p","true.po"))

result <- parLapply(cl,1:20,function(j){
  
  if (j <= 10){
    mc <- true.po[[j]]
  } else {
    mc <- t(true.po[[j-10]])
  }
  
  b <- rgeom.bucket.from.po(mc,n.samples=N,p=.5,suborder=T,noise.prob=p)
  
  chain <- rposterior.bucket.mean(n=n,b=b,n.samples=n.samples,burn=burn,thin=thin,draw=F,return.lsm=T,r=.5,noise.prob=p)
  
  pos.po <- chain$mean
  
  ham.dist <- numeric(101)
  
  for (i in 0:100){
    q.consensus <- consensus.po2(pos.po,p=i/100)
    
    if (check.dag(q.consensus)){
      ham.dist[i+1] <- hamming.dist(q.consensus,mc)/(n*(n-1)/2+sum(mc))
    } else {
      ham.dist[i+1] <- NA
    }
  }
  
  ham.dist
})

stopCluster(cl)

result <- do.call(rbind,result)
```

```{r}
p.values <- (0:100)/100

plot(p.values,result[1,],type="l",xlab="p",ylab="Relative Hamming distance",ylim=range(result,na.rm=T),col=adjustcolor(1,alpha=.85))

for (i in 1:10){
  lines(p.values,result[i,],col=adjustcolor(i,alpha=.85))
  lines(p.values,result[i+10,],col=adjustcolor(i,alpha=.85))
}
```


20 chains targeting different h_0
```{r}
n <- 24L; N <- 30; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05

cl <- makeCluster(20)

clusterExport(cl,c("n","N","burn","thin","n.samples","p"))

clusterEvalQ(cl,{
  library(MASS)
  library(mnem)
  library(igraph)
  library(Rgraphviz)
  library(graph)
  library(coda)
  library(lecount)
  library(partitions)
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
  
  check.dag <- function(mc){!any(mc+t(mc)==2)}
})

clusterSetRNGStream(cl,11)

result <- parLapply(cl,1:20,function(j){
  
  m <- rZPO(n)
  mc <- my.transitive.closure(m)
  mr <- transitive.reduction(m)
  
  b <- rgeom.bucket.from.po(mc,n.samples=N,p=.5,suborder=T,noise.prob=p)
  
  m0 <- rZPO(n)
  chain <- rposterior.bucket.mean(n=n,b=b,n.samples=n.samples,burn=burn,thin=thin,draw=F,return.lsm=T,r=.5,noise.prob=p,m=m0)
  
  pos.po <- chain$mean
  
  ham.dist <- numeric(101)
  
  for (i in 0:100){
    q.consensus <- consensus.po2(pos.po,p=i/100)
    
    if (check.dag(q.consensus)){
      ham.dist[i+1] <- hamming.dist(q.consensus,mc)/(n*(n-1)/2+sum(mc))
    } else {
      ham.dist[i+1] <- NA
    }
  }
  
  ham.dist
})

stopCluster(cl)

result <- do.call(rbind,result)
```

```{r}
jpeg("20_relative_hamming_distance.jpeg",width=1800,height=1200,res=200)

p.values <- (0:100)/100

plot(p.values,result[1,],type="l",xlab="q",ylab="Relative Hamming distance",ylim=range(result,na.rm=T),col=adjustcolor(1,alpha=.85))

for (i in 2:nrow(result)){
  lines(p.values,result[i,],col=adjustcolor(i,alpha=.85))
}

dev.off()
```



Simulations for relative hamming dist vs N 
```{r}
#m=10
n <- 10L; N <- 40; burn <- 1e4; thin <- 1; n.samples <- 1e5; p <- 0.05

cl <- makeCluster(10)

clusterEvalQ(cl, {
  library(MASS)
  library(mnem)       # needed for transitive.reduction/closure
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)       # for MCMC output analysis
  library(lecount)    # count linear extensions of a PO
  library(partitions) # used by dimension functions
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
})


clusterExport(cl, c("n","N","burn","thin","n.samples","p","buckets.10","true.po.10"))

ham.dist.10.all <- parLapply(cl, 1:10, function(j){
  
  q.consensus.10 <- vector("list",8)
  pos.po.10 <- vector("list",8)
  ham.dist.10 <- numeric(8)
  
  for (i in 1:8){
    chain.10 <- rposterior.bucket(n=n, b=buckets.10[1:(5*i)], n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm=T, r=.5, noise.prob=p)
    pos.po.10[[i]] <- mean.po(chain.10$samples)
    q.consensus.10[[i]] <- consensus.po2(pos.po.10[[i]],p=0.5)
    ham.dist.10[i] <- hamming.dist(q.consensus.10[[i]],true.po.10)
  }
  
  ham.dist.10
})

stopCluster(cl)

ham.dist.10.all <- do.call(rbind,ham.dist.10.all)


ham.mean.10 <- apply(ham.dist.10.all,2,mean)
ham.sd.10 <- apply(ham.dist.10.all,2,sd)
ham.se.10 <- ham.sd.10/sqrt(10)

ham.lower.10 <- ham.mean.10-qt(.975,9)*ham.se.10
ham.upper.10 <- ham.mean.10+qt(.975,9)*ham.se.10

#m=20
n <- 20L; N <- 40; burn <- 1e4; thin <- 1; n.samples <- 1e5; p <- 0.05

cl <- makeCluster(10)

clusterExport(cl, c("n","N","burn","thin","n.samples","p","buckets.20","true.po.20"))

clusterEvalQ(cl, {
  library(MASS)
  library(mnem)       # needed for transitive.reduction/closure
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)       # for MCMC output analysis
  library(lecount)    # count linear extensions of a PO
  library(partitions) # used by dimension functions
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
})


ham.dist.20.all <- parLapply(cl, 1:10, function(j){
  
  q.consensus.20 <- vector("list",8)
  pos.po.20 <- vector("list",8)
  ham.dist.20 <- numeric(8)
  
  for (i in 1:8){
    chain.20 <- rposterior.bucket(n=n, b=buckets.20[1:(5*i)], n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm=T, r=.5, noise.prob=p)
    pos.po.20[[i]] <- mean.po(chain.20$samples)
    q.consensus.20[[i]] <- consensus.po2(pos.po.20[[i]],p=0.5)
    ham.dist.20[i] <- hamming.dist(q.consensus.20[[i]],true.po.20)
  }
  
  ham.dist.20
})

stopCluster(cl)

ham.dist.20.all <- do.call(rbind,ham.dist.20.all)


ham.mean.20 <- apply(ham.dist.20.all,2,mean)
ham.sd.20 <- apply(ham.dist.20.all,2,sd)
ham.se.20 <- ham.sd.20/sqrt(10)

ham.lower.20 <- ham.mean.20-qt(.975,9)*ham.se.20
ham.upper.20 <- ham.mean.20+qt(.975,9)*ham.se.20

#m=30
n <- 30L; N <- 40; burn <- 1e4; thin <- 1; n.samples <- 1e5; p <- 0.05

cl <- makeCluster(10)

clusterExport(cl, c("n","N","burn","thin","n.samples","p","buckets.30","true.po.30"))

clusterEvalQ(cl, {
  library(MASS)
  library(mnem)       # needed for transitive.reduction/closure
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)       # for MCMC output analysis
  library(lecount)    # count linear extensions of a PO
  library(partitions) # used by dimension functions
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
})


ham.dist.30.all <- parLapply(cl, 1:10, function(j){
  
  q.consensus.30 <- vector("list",8)
  pos.po.30 <- vector("list",8)
  ham.dist.30 <- numeric(8)
  
  for (i in 1:8){
    chain.30 <- rposterior.bucket(n=n, b=buckets.30[1:(5*i)], n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm=T, r=.5, noise.prob=p)
    pos.po.30[[i]] <- mean.po(chain.30$samples)
    q.consensus.30[[i]] <- consensus.po2(pos.po.30[[i]],p=0.5)
    ham.dist.30[i] <- hamming.dist(q.consensus.30[[i]],true.po.30)
  }
  
  ham.dist.30
})

stopCluster(cl)

ham.dist.30.all <- do.call(rbind,ham.dist.30.all)
```

Relative hamming dist vs N plots
```{r}
N.values <- 5*(1:8)

mean.10 <- apply(ham.dist.10.all,2,mean)/(10*9/2+sum(true.po.10))
se.10 <- apply(ham.dist.10.all,2,sd)/(sqrt(10)*(10*9/2+sum(true.po.10)))
ci.10 <- qt(.975,9)*se.10

mean.20 <- apply(ham.dist.20.all,2,mean)/(20*19/2+sum(true.po.20))
se.20 <- apply(ham.dist.20.all,2,sd)/(sqrt(10)*(20*19/2+sum(true.po.20)))
ci.20 <- qt(.975,9)*se.20

mean.30 <- apply(ham.dist.30.all,2,mean)/(30*29/2+sum(true.po.30))
se.30 <- apply(ham.dist.30.all,2,sd)/(sqrt(10)*(30*29/2+sum(true.po.30)))
ci.30 <- qt(.975,9)*se.30

jpeg("relative_hamming_distance.jpeg",width=1800,height=1200,res=200)

plot(N.values,mean.10,type="b",pch=16,col="red",ylim=range(c(mean.10-ci.10,mean.10+ci.10,mean.20-ci.20,mean.20+ci.20,mean.30-ci.30,mean.30+ci.30)),xlab="N",ylab="Relative Hamming distance")
arrows(N.values,mean.10-ci.10,N.values,mean.10+ci.10,angle=90,code=3,length=.05,col="red")

lines(N.values,mean.20,type="b",pch=17,col="blue")
arrows(N.values,mean.20-ci.20,N.values,mean.20+ci.20,angle=90,code=3,length=.05,col="blue")

lines(N.values,mean.30,type="b",pch=15,col="darkgreen")
arrows(N.values,mean.30-ci.30,N.values,mean.30+ci.30,angle=90,code=3,length=.05,col="darkgreen")

legend("topright",legend=c("m = 10","m = 20","m = 30"),pch=c(16,17,15),lty=1,col=c("red","blue","darkgreen"))

dev.off()
```



Chains that target an empty a total order, 8 each
```{r}
#8 chains targeting the empty po, m=24
n <- 24L; N <- 30; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05

cl <- makeCluster(10)

clusterExport(cl, c("n","N","burn","thin","n.samples","p","buckets.emp","empty.po"))

clusterEvalQ(cl, {
  library(MASS)
  library(mnem)       # needed for transitive.reduction/closure
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)       # for MCMC output analysis
  library(lecount)    # count linear extensions of a PO
  library(partitions) # used by dimension functions
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
})


ham.dist.emp.all <- parLapply(cl, 1:10, function(j){
  
  q.consensus.emp <- vector("list",8)
  pos.po.emp <- vector("list",8)
  ham.dist.emp <- numeric(8)
  
  for (i in 1:8){
    m0 <- rZPO(n)
    chain.emp <- rposterior.bucket.mean(n=n, b=buckets.emp, n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm=T, r=.5, noise.prob=p,m=m0)
    pos.po.emp[[i]] <- chain.emp$mean
    q.consensus.emp[[i]] <- consensus.po2(pos.po.emp[[i]],p=0.5)
    ham.dist.emp[i] <- hamming.dist(q.consensus.emp[[i]],empty.po)
  }
  
  ham.dist.emp
})

stopCluster(cl)

ham.dist.emp.all <- do.call(rbind,ham.dist.emp.all)

#8 chains targeting 1:24, m=24
n <- 24L; N <- 30; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05

cl <- makeCluster(10)

clusterExport(cl, c("n","N","burn","thin","n.samples","p","buckets.total","total.order"))

clusterEvalQ(cl, {
  library(MASS)
  library(mnem)       # needed for transitive.reduction/closure
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)       # for MCMC output analysis
  library(lecount)    # count linear extensions of a PO
  library(partitions) # used by dimension functions
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
})


ham.dist.total.all <- parLapply(cl, 1:10, function(j){
  
  q.consensus.total <- vector("list",8)
  pos.po.total <- vector("list",8)
  ham.dist.total <- numeric(8)
  
  for (i in 1:8){
    m0 <- rZPO(n)
    chain.total <- rposterior.bucket.mean(n=n, b=buckets.total, n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm=T, r=.5, noise.prob=p,m=m0)
    pos.po.total[[i]] <- chain.total$mean
    q.consensus.total[[i]] <- consensus.po2(pos.po.total[[i]],p=0.5)
    ham.dist.total[i] <- hamming.dist(q.consensus.total[[i]],total.order)
  }
  
  ham.dist.total
})

stopCluster(cl)

ham.dist.total.all <- do.call(rbind,ham.dist.total.all)
```

Figures about the chains targeting the empty order and total order 
```{r}
mean(ham.dist.emp.all)
qt(.95,df=80-1)*sd(ham.dist.emp.all)/sqrt(80)

mean(ham.dist.total.all)
qt(.95,df=80-1)*sd(ham.dist.total.all)/sqrt(80)

mean(ham.dist.emp.all)/23/12
qt(.95,df=80-1)*sd(ham.dist.emp.all)/sqrt(80)/23/12

mean(ham.dist.total.all)/23/24
qt(.95,df=80-1)*sd(ham.dist.total.all)/sqrt(80)/23/24

mean.shallow <- mean(relations[1:5])
ci.shallow <- qt(.975,4)*sd(relations[1:5])/sqrt(5)

mean.high <- mean(relations[6:10])
ci.high <- qt(.975,4)*sd(relations[6:10])/sqrt(5)

mean.shallow
ci.shallow

mean.high
ci.high
```

Plots of .5-consensus of chain targeting total order and empty order
```{r}
showDAG(q.consensus.total[[1]],vertex.color="white",vertex.size=10,edge.arrow.size=0.5)

showDAG(q.consensus.emp[[1]],vertex.color="white",vertex.size=10,edge.arrow.size=0.5)
```


4.4 Primate data
```{r}
set.seed(10)

results4 <- vector("list",8)
time.taken <- numeric(8)
mean.order <- vector("list",8)

library(parallel)

cl <- makeCluster(8)


# load libraries and source files on each worker
clusterEvalQ(cl, {
  library(MASS)
  library(mnem)       # needed for transitive.reduction/closure
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)       # for MCMC output analysis
  library(lecount)    # count linear extensions of a PO
  library(partitions) # used by dimension functions
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
})


# independent random-number streams
clusterSetRNGStream(cl, 10)

n <- 24L; N <- 30; burn <- 1e5; thin <- 1; n.samples <- 1e6; noise.prob <- .05
#m <- code1.m
#mc <- my.transitive.closure(m); true.po <- mc;
#b <- rgeom.bucket.from.po(mc,n.samples = N,p=.5,suborder=T); 
#b.mc <- bucket2mc.full(b,20)

clusterExport(cl, c(
  "n",
  "N",
  "burn",
  "thin",
  "n.samples",
  "b.primates",
  "noise.prob"
))

results4 <- parLapply(cl, 1:8, function(i){
  
  
  m <- rZPO(24)
  mean.i <- rposterior.bucket.mean(n=n, b=b.primates, n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm = T, r=.5, m=m, noise.prob = noise.prob) 
  
  mean.i
  
})


```

Analyzing the primates mcmc
```{r}
#dissimilarity matrix records the pairwise Hamming distance between the 8 .5-consensus partial order from the primate simulations
consensus <- vector("list",8)

for (i in 1:8){
  consensus[[i]] <- consensus.po2(results4[[i]]$mean,p=.5)
}

dissimilarity <- matrix(0,8,8)

for (i in 1:8){
  for (j in 1:8){
    dissimilarity[i,j] <- hamming.dist(consensus[[i]],consensus[[j]])
  }
}

dissimilarity
rowSums(dissimilarity)


#primate ranking
for (i in 1:8) {
  primate.cons <- transitive.reduction(consensus.po2(results4[[i]]$mean,p=.5))
  primate.names <- c("Pan","Pongo","Gorilla","Hylobates","Presbytis","Macaca","Mandrillus","Cercopithecus","Papio","Cercocebus","Miopithecus","Ateles","Aotus","Lagothrix","Callithrix","Saimiri","Cebus","Eulemur","Nycticebus","Phaner","Varecia","Microcebus","Galago","Lemur")
  
  par(mar=c(5,4,4,16),xpd=NA)
  showDAG(primate.cons,vertex.label=1:24,vertex.color="white",vertex.size=15,edge.arrow.size=.5)
  title("Consensus Order of Primate Cognitive Rankings")
  usr <- par("usr"); x1 <- usr[2]+.08*(usr[2]-usr[1]); x2 <- usr[2]+.32*(usr[2]-usr[1]); y <- seq(usr[4]-.12*(usr[4]-usr[3]),usr[3]+.12*(usr[4]-usr[3]),length.out=12)
  text(x1,y,paste(1:12,primate.names[1:12]),adj=0,cex=.65); text(x2,y,paste(13:24,primate.names[13:24]),adj=0,cex=.65); text(x1,usr[4]+.02*(usr[4]-usr[3]),"Primate key",adj=0,cex=.75,font=2)
}
  
jpeg("consensus_order_primate_8.jpeg",width=1800,height=1000,res=250)

i <- 8

primate.cons.1 <- transitive.reduction(consensus.po2(results4[[i]]$mean,p=1/3))
primate.cons.2 <- transitive.reduction(consensus.po2(results4[[i]]$mean,p=.5))

primate.names <- c("Pan","Pongo","Gorilla","Hylobates","Presbytis","Macaca","Mandrillus","Cercopithecus","Papio","Cercocebus","Miopithecus","Ateles","Aotus","Lagothrix","Callithrix","Saimiri","Cebus","Eulemur","Nycticebus","Phaner","Varecia","Microcebus","Galago","Lemur")

par(mfrow=c(1,3),mar=c(2,2,1,2),xpd=NA)

showDAG(primate.cons.1,vertex.label=1:24,vertex.color="white",vertex.size=15,edge.arrow.size=.5)

showDAG(primate.cons.2,vertex.label=1:24,vertex.color="white",vertex.size=15,edge.arrow.size=.5)

plot.new()
usr <- par("usr")
text(.05,.95,"Primate key",adj=0,cex=.9,font=2)
text(.05,seq(.88,.12,length.out=12),paste(1:12,primate.names[1:12]),adj=0,cex=.75)
text(.55,seq(.88,.12,length.out=12),paste(13:24,primate.names[13:24]),adj=0,cex=.75)

dev.off()
```

4.3. code finding how number of edges in h0 affects the shape of the hamming dist
```{r}
n <- 24L; N <- 30; burn <- 1e5; thin <- 1; n.samples <- 1e6; p <- 0.05

cl <- makeCluster(10)

clusterExport(cl, c("n","N","burn","thin","n.samples","p","buckets.emp","empty.po"))

clusterEvalQ(cl, {
  library(MASS)
  library(mnem)
  library(igraph) 
  library(Rgraphviz)
  library(graph) 
  library(coda)
  library(lecount)
  library(partitions)
  
  setwd(getwd())
  
  source(file="pofun.R")
  source(file="pofun_aux.R")
  source(file="modelfun.R")
  source(file="dimfun.R")
  source(file="my_code.R")
  source(file="code data.R")
})

clusterSetRNGStream(cl,10)

mean.dep <- parLapply(cl, 1:10, function(j){
  
  if (j <= 5){
    repeat {
      m0 <- rZPO(n)
      if (dag.depth(m0,n) <= 7) break
    }
  } else {
    repeat {
      m0 <- rZPO(n)
      if (dag.depth(m0,n) >= 17) break
    }
  }
  
  buckets.emp <- rgeom.bucket.from.po(m0,n.samples = N,p=.5,suborder=T,noise.prob = p)
  
  chain.emp <- rposterior.bucket.mean(n=n, b=buckets.emp, n.samples=n.samples, burn=burn, thin=thin, draw=F, return.lsm=T, r=.5, noise.prob=p, m=m0)
  
  list(
    target=m0,
    mean=chain.emp$mean
  )
  
})

stopCluster(cl)


q.consensus.dep <- vector("list",10)
ham.dist.dep <- matrix(NA,10,101)

for (i in 1:10){
  
  q.consensus.dep[[i]] <- consensus.po2(mean.dep[[i]]$mean,p=0.5)
  
  for (j in 0:100){
    q.consensus <- consensus.po2(mean.dep[[i]]$mean,p=j/100)
    ham.dist.dep[i,j+1] <- hamming.dist(q.consensus,mean.dep[[i]]$target)
  }
}

```

Plots of Hamming dist against q on diff number of edges
```{r}
p.values <- (0:100)/100

ham.dist.dep.rel <- matrix(NA,10,101)

for (i in 1:10){
  m0 <- mean.dep[[i]]$target
  max.ham <- n*(n-1)/2 + sum(m0)
  ham.dist.dep.rel[i,] <- ham.dist.dep[i,]/max.ham
}


jpeg("relative_hamming_shallow_depth.jpeg",width=1800,height=1200,res=200)

plot(p.values,ham.dist.dep.rel[1,],type="l",xlab="q",ylab="Relative Hamming distance",ylim=range(ham.dist.dep.rel[1:5,],na.rm=T),col=1)

for (i in 2:5){
  lines(p.values,ham.dist.dep.rel[i,],col=i)
}

dev.off()


jpeg("relative_hamming_high_depth.jpeg",width=1800,height=1200,res=200)

plot(p.values,ham.dist.dep.rel[6,],type="l",xlab="q",ylab="Relative Hamming distance",ylim=range(ham.dist.dep.rel[6:10,],na.rm=T),col=1)

for (i in 7:10){
  lines(p.values,ham.dist.dep.rel[i,],col=i-5)
}

dev.off()
```

```{r}
save(mean.dep,ham.dist.dep,ham.dist.dep.rel,relations,results4,
     file="posim_results.RData")
```

